Analyzing the Effects of the NBA COVID Bubble on the NBA Playoffs

### 2020-11-02 Manuscript/NBABubbleAnalysis.Rmd
Update NBABubbleAnalysis.Rmd

At least some of that improvement from away teams came from significantly higher 
two point efficiency. This corresponds with the conclusion from @Harris,
where they found home teams are best suited to capitalize on advantages from two point
shots. Normally, by shooting more 2 themselves and forcing away teams to shoot more 2
they home team benefits from increasing home-court advantage. However, with away teams
significantly improving two point shooting in the bubble this strategy was no longer 
viable and home-court advantage disappeared.

>>>>

At least some of that improvement from away teams came from significantly higher 
two point efficiency. This corresponds with the conclusion from @Harris,
where they found home teams are best suited to capitalize on advantages from two point
shots. Normally, by shooting more two pointers themselves and forcing away teams to 
shoot more two pointers the home team benefits from increasing effects of home-court advantage. 
However, with away teams significantly improving two point shooting in the bubble this strategy 
was no longer viable and home-court advantage disappeared.
